A New Metric for the Analysis of Swarms

### 2018-07-31 paper.tex
More Updates

\textit{Centroidal} analysis: The centroid of a swarm is its \textit{centre of mass} as shown in Equation~\ref{eq:Centroid1}. This is often used as a reference point to determine the path of a swarm or to measure how agents are arranged within a swarm's structure. Navarro et al. use the centroid to produce a \textit{Mean Distance from the Boundary to the Center of the Group} metric. This metric takes the distance of each agent from the centroid and calculates the mean and the deviation to produce a measure~\cite{NIM:09}. Gazi and Passino also use this technique when analysing the stability of a swarm based on agent distribution~\cite{GP:11}. Gazi and Passino also use the centroid when analysing the stability of a swarm which is designed to maintain its position by analysing the changes in the centroids position over time~\cite{GP:04}.

The centroid of the swarm is determined by taking the coordinate position of each agent and calculating the mean of the $x$ and $y$ positions as shown in Equation~\ref{eq:Centroid1}.

\begin{equation}\label{eq:Centroid1}
C_s = \frac{1}{\card{S}}\mathlarger{\sum_{b' \in S}} b'
\end{equation}

>>>>

\textit{Centroidal} analysis: The centroid of a swarm is its \textit{centre of mass} as shown in Figure~\ref{com} as a red cross. This is often used as a reference point to determine the path of a swarm or to measure how agents are arranged within a swarm's structure. Navarro et al. use the centroid to produce a \textit{Mean Distance from the Boundary to the Center of the Group} metric~\cite{NIM:09}. This metric takes the distance of each agent from the centroid and calculates the mean and the deviation to produce a measure. Gazi and Passino also use this technique when analysing the stability of a swarm based on agent distribution~\cite{GP:11}. Gazi and Passino also use the centroid when analysing the stability of a swarm which is designed to maintain its position by analysing the changes in the centroids position over time~\cite{GP:04}.

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=4.5cm]{figures/com}
{Swarm Centre of Mass.\label{com}}

The centroid of the swarm ($C_s$) is determined by taking the coordinate position of each agent and calculating the mean positions as shown in Equation~\ref{eq:Centroid1} where $b_{coord}$ is each agents coordinates and $S$ is the set of agents that make up the swarm.

\begin{equation}\label{eq:Centroid1}
C_s = \frac{1}{\card{S}}\mathlarger{\sum_{b \in S}} b_{coord}
\end{equation}
